Towards Transparency and Open Science

### 2023-07-21 manuscript.Rmd
include pdfx latex package

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
author: "Aaron Peikert"
output:
  bookdown::pdf_document2:
    includes:
      in_header: "preamble.tex"
    latex_engine: "lualatex"
    toc: true
    number_sections: false
    keep_tex:  true
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
# asymetric geometry is set after/in frontmatter.md
geometry: "left=4cm, right=4cm, top=3cm, bottom=5cm, bindingoffset=7mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}\\\\textsc{Abstract:}', readLines('abstract.md'), '\\\\vspace{1mm}\\\\par \\\\textsc{Zusammenfassung:}\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  packages:
    - gert
    - aaronpeikert/repro@5075336
  files:
    - zusammenfassung.md
    - abstract.md
    - frontmatter.md
    - cover.pdf
    - preamble.tex
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
    - lualatex-math
    - luatexbase
    - titling
  apt:
    - git
    - rsync
---

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
author: "Aaron Peikert"
output:
  bookdown::pdf_document2:
    includes:
      in_header: "preamble.tex"
    latex_engine: "lualatex"
    toc: true
    number_sections: false
    keep_tex:  true
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
# asymetric geometry is set after/in frontmatter.md
geometry: "left=4cm, right=4cm, top=3cm, bottom=5cm, bindingoffset=7mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}\\\\textsc{Abstract:}', readLines('abstract.md'), '\\\\vspace{1mm}\\\\par \\\\textsc{Zusammenfassung:}\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  packages:
    - gert
    - aaronpeikert/repro@5075336
  files:
    - zusammenfassung.md
    - abstract.md
    - frontmatter.md
    - cover.pdf
    - preamble.tex
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
    - lualatex-math
    - luatexbase
    - titling
    - pdfx
  apt:
    - git
    - rsync
---
